### 2021-04-24 README.Rmd
got the badge to work in the readme

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?token=zA4xhwrbzL7YLqiktuAB&branch=main)](https://travis-ci.com/srmatth/mshap)
<!-- badges: end -->
